---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# PointFore

The goal of PointFore is to estimate specification models for the state-dependent level of an optimal quantile/expectile forecast.

Wald Tests and the test of overidentifying restrictions are implemented. Ploting of the estimated specification model is possible.

Based on "Interpretation of Point Forecasts" by Patrick Schmidt, Matthias Katzfuss, and Tilmann Gneiting, 2018.

## Installation

You can install PointFore from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Schmidtpk/PointFore")
```

## Example

This is a basic example which shows you how to evaluate which quantile is forecsted by the Greenbook GDP forecats:

```{r example}
library(PointFore)
res <- estimate.functional(Y=GDP[,1],X=GDP[,2])
summary(res)
plot(res)
```


```{r example with state-dependence}
res <- estimate.functional(Y=GDP[,1],X=GDP[,2],
                           model=logistic,theta0=c(0,0),
                           stateVariable = GDP[,2])
summary(res)
plot(res)
```
